Trauma treatment delay

### 2023-11-28 manuscriptlongversion.Rmd
text

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model, such as making them into factors, renaming outcomes in
the database and removing unknown values.

@@

For the missing hospital values in GCS, RR and SBP, values from EMT
personnel were used

The dependent variable is OFI_delay, which is the presence of the ofi
delayed treatment.

@@

The biases that might have been present in this study would be selection
bias and misclassification bias.

>>>>

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model, such as making them into factors, renaming outcomes in
the database and removing unknown values. The variables were either
binary or continuous.

@@

For the missing hospital values in GCS, RR and SBP, values from EMT
personnel were used. This was accomplished by identifying missing data
in the column for the hospital value of the variable and, if available,
replacing the row in the dataset with the prehospital value. If a
prehospital value is missing, the patient is excluded from the study.

The logistical regression is run through Rstudio using the glm command.
To make the tables, the package gtsummary was used to visualize the
adjusted and unadjusted regression, then merging the two tables into
one.

@@

The biases that might have been present in this study would be selection
bias and misclassification bias. Our aim is to make this applicable to
the whole trauma patient
